Market Simulator

### 2020-08-07 analysis/05_market_simulator.Rmd
Added Persona tabs. need reactive element for personas

Market Share Per Persona 
--------------------------------------

@@

@@

Organization Breakdown {.tabset .tabset-fade}
--------------------------------------------------
### Amnesty International

@@

  gauge(ai_rate,
        min = 0,
        max = 100,
        gaugeSectors(colors = "#FFC30B"),
        symbol = "%")
})
```

### Greenpeace

@@

### Oxfam

@@

### Redcross

@@

>>>>

Market Share Per Persona {data-height=600}
--------------------------------------

@@

  ggplotly(df %>% filter(Type == "Market Share") %>% 
             ggplot(aes(y = Value, x = Organization, fill = Persona)) +
             geom_bar(position = "dodge", stat = "identity") +
             labs(x="") + 
             scale_fill_manual(values = c( "#FFC30B", "#3fad48", "#006633", "#660000")) +
             theme(legend.position = "none")
    )
})

@@

Organization Breakdown {.tabset .tabset-fade}
--------------------------------------------------
### Org 1

@@

  gauge(ai_rate,
        min = 0,
        max = 100,
        gaugeSectors(colors = "#FFC30B"),
        symbol = "%")
})

renderGauge({
  choice = df()
  persona = p_beta2 # Choose the persona

  gauge(ai_rate,
        min = 0,
        max = 100,
        gaugeSectors(colors = "#3fad48"),
        symbol = "%")
})

renderGauge({
  choice = df()
  persona = p_beta3 # Choose the persona

  gauge(ai_rate,
        min = 0,
        max = 100,
        gaugeSectors(colors = "#006633"),
        symbol = "%")
})
```

### Org 2

@@

### Org 3

@@

### Org 4

@@

### Persona 1

```{r persona 1 inputs}

### Persona 2

```{r persona 2 inputs}

### Persona 3

```{r persona 3 inputs}
